### 2017-11-06 monograph/thesis/chapters/good_practices.tex
Fixed Sublime Text LatexTools (Log parsing issues. Disregard unless
something else is wrong.), issue:
(Log parsing issues. Disregard unless something else is wrong.)
https://github.com/SublimeText/LaTeXTools/issues/1216
Split the object_beautifier.tex The Problem section to other
related chapters.
Created the reference Tracking Changes, trackingChanges.
Created the section Semantic linefeed links on good_practices.tex

@@

\end{englishtext}

>>>>

    \citeonline{trackingChanges},

@@

    \section{Semantic linefeed}

    http://rhodesmill.org/brandon/2012/one-sentence-per-line/
    https://www.google.com.br/search?q=semantic+linefeeds
    https://news.ycombinator.com/item?id=4642395
    https://en.wikipedia.org/wiki/Wikipedia:Don%27t_use_line_breaks
    https://erambler.co.uk/blog/semantic-linefeeds/
    https://vi.stackexchange.com/questions/9828/insert-a-newline-after-punctuations
    https://blog.doismellburning.co.uk/semantic-linebreaks/
    https://scott.mn/2014/02/21/semantic_linewrapping/
